%!TEX root = ../Thesis.tex
\chapter{Related work}
\label{chap:relatedWork}
It is widely believed that crosstalk is stereoscopic or automultiscopic screen results in reduced visual comfort, reduced disparity range, reduced contrast and most importantly, reduction of perceived depth. However, the literature is not thorough about how the  crosstalk effects the perceived depth. Wilcox et al \cite{wilcox2003determinants} performed a large scale experiment in which 77 observers were shown a small stereo footage in two commercial large-formate 3D theaters. The typical stereo degradations in theaters that were considered were crosstalk (ghosting), brightness, and the other qualities of 3D. The test subjects were asked to evaluate which one those degradations affected their experience the most. 75\% of the subjects reported that ghosting was the most prominent in degrading their viewing experience.
\textcolor{red}{Write something more.}

Below is a review of some of the work that has previously been done in this area.

\section{Effects of crosstalk on perceived depth}
K.C.Huang et al \cite{huang2003crosstalk} performed intensive experiments in order to obtain a threshold for the system crosstalk that on average will not mitigate the effects of the depth from disparity. Since the viewer crosstalk is dependent upon the system crosstalk and the local contrast of the desperate object in the image, a uniform level of crosstalk (same crosstalk all over the screen which does not change with time) should not have the same effect on all kinds of stereo images. This is because the HVS sensitivity to detect the change in luminance follows Webber's law \cite{webber}. Which means that compared to areas of the image with high local contrast, the HVS is more tolerable towards crosstalk where the local contrast is low. Based on this idea and the fact that the HVS also uses monocular cues to estimate depth, they performed experiments using a Wheatstone setup (similar to ours) and a set of images with various contrasts and disparities to finally propose that 10\% system crosstalk is the maximum crosstalk that will mostly not affect the depth estimation via disparity. We observed in our experiments that even though above 10\% of crosstalk heavily degrades the perceived depth, it still does not result in total depth loss due to disparity. On our high contrast images, we determined that crosstalk level of greater than 16\% usually resulted in the total loss of depth.

Ghosted images due to crosstalk as seen in figure \textcolor{red}{make figure somewhere} can be seen as locally decreasing the contrast of the desperate object. Rohaly et al \cite{rohaly1999effects} determined the effects that contrast exhibits on the stereoscopically perceived depth. She concluded that decrease in contrast made the objects (crossed and uncrossed) appear to be farther from the viewers. Which means that the crossed objects with decreased contrast appeared to be moving towards the horoptor whereas the uncrossed objects appeared to be moving away from the horopter. She also found that monocular contrast reduction amplified this effect more compared to the contrast reduction in both eyes \textcolor{red}{Mention this in the discussion of the results}. It was also argued that the contrast exerts its effect before or at the extraction of depth.

The work that is most relevant to our work was performed by Tsirlin et al. They quantified the amount of depth loss due to crosstalk on objects of various dimensions and disparities. In 2011 \cite{tsirlin2011effect}, they performed experiments where the test subjects were asked to specify the observed depth at various depths of a stimulus (a rectangular structure) the width of which was chosen to be such that at any disparity, the ghost would not be completely separated. The luminance of the structure was set to be the maximum (white) on a completely black background. The subjects reported the observed depth via a slider bar located under the stimulus without any reference. \textcolor{red}{insert the stimulus and the graph here.}. They observed that the perceived depth decreased with the increase in crosstalk as well as increase in disparity. In the second part of the experiment, they observed the effect of crosstalk on binocular occlusion and found out that effect of crosstalk on the perceived depth due to occlusion was even more swear. In 2012 \cite{tsirlin2012effect}, they performed similar experiments to observe the effects of crosstalk on thin structures where the ghost is always completely separated from the stimulus (which is usually the case with vertical thin structures present at a significant distance from the plane of focus). Again they found that observed depth degrades significantly as the disparity or the crosstalk level was increased. However this time the degradation was observed to be higher than the case where the ghosts always overlapped the stimulus. One problem with these experiments is that the stimuli are presented as a uniformly luminant objects on a black background where there is no other depth cue present. This is usually not the case with the complex scene that we typically observe in 3D movies. We observed in our test experiments that in such scenes the depth of the stimuli was extremely hard to perceive even at moderately high disparities. Tsirlin also observed that the perceived depth degraded with disparity even in the base case i.e. the case where crosstalk was set to zero. This is not usually the case in complex scenes. Secondly, there was no reference used and the subjects were simply asked to report the observed depth via a slider bar that was controlled with a mouse. This `rating' setup can be problematic because it can not be guaranteed that all the subjects were rating the same depth equally \textcolor{red}{write something better}. And finally, the relation of the stimulus width to the perceived depth at different disparities was not determined which we think is also necessary \textcolor{red}{why?}.

Tsirlin et al \cite{tsirlin2012crosstalk} again performed similar experiments but this time with complex natural scenes. The subjects were shown a complex scenes with the objects of interest marked by arrows. Later, they were shown the exact same images with crosstalk induced and were asked to rate the depth difference they observed between those two objects. The results again concluded that the perceived depth difference decreased as the theoretical depth difference between the objects of interest and the crosstalk increased.\textcolor{red}{write some criticism}.

\section{Depth resolution mechanisms in HVS}
% \subsection{Banks and cormacks work}
It is clear that crosstalk in stereoscopic displays reduce the perceived depth proportional to the level of crosstalk and the disparity of an object. However, in order to understand why the perceived depth is degraded, we had to look into some literature where the depth information extraction by the HVS from disparity is investigated.

It is widely believed that the HVS uses some kind of cross-correlation of retinal patches between the two eyes in order to determine the location (or in other words the disparity) at which some object is located in a retinal image with respect to the other. Cormack \cite{cormack1991interocular} investigated the binocular fusion process with respect to contrast of the stimuli and concluded that the binocular fusion was dependent upon the contrast and the strength of the binocular cross-correlation profile of the stimuli. The cross-correlation was computed as a function of image luminance. The stimuli used in his experiments were random dot stereograms in which the number of white dots matching between the left and the right eye images at some disparity represented the interocular correlation. He concluded that at low contrast, the binocular fusion increased when as the contrast of the stimuli (white dots in the stereograms) increased. The reason behind this can be seen in figure \textcolor{red}{insert fig 6 } where the cross-correlation (interocular correlation IOC \index{IOC}) profiles at different contrasts has been plotted. The peaks in these profiles represents the disparity at which the two images matched the most. It is clear that as the contrast decreases, the distinctness of the these peaks also degrades which might make it difficult for the HVS to identify. Same is also true if noise is added to the images as seen in figure \textcolor{red}{insert figure 7.}. This can be one of the reasons for the degradation of the perceived depth in ghosted images as the ghost (due to crosstalk) in an image is just a low contrast version of the stimulus added into the image at some disparity effectively reducing the overall contrast. We used these finding in deriving our own model for the HVS that will be explained in chapter 5.

Filippini and Banks \cite{filippini2009limits} explained the limits of stereopsis and modeled them by using windowed interocular cross-correlation. The neighborhood of each pixel in one stereo images (say left) was weighed by an isotropic Gaussian window followed by horizontally displacing a similar window in the right eye image. For each displacement, the cross-correlation of the windowed patched was computed. The disparity was obtained at the displacement value where the maximum correlation for the patches was obtained. The 2D cross-correlation formula used was as seen in equation \ref{eq:ccr}.

\begin{equation}
c(\delta_x) = \frac{ \sum\limits_{(x,y) \in W_L} [(L(x,y) - \mu_L)(R(x-\delta_x, y) - \mu_R)] }{\sqrt{\sum\limits_{(x,y) \in W_L}(L(x,y) - \mu_L)^2} \sqrt{\sum\limits_{(x,y) \in W_R}(R(x-\delta_x, y)- \mu_R)^2}}
\label{eq:ccr}
\end{equation}

Where L(x,y) and R(x,y) are the image intensities for the left and right eye, W\textsubscript{L} and W\textsubscript{R} are the Gaussian windows applied to the images, $\mu\textsubscript{L}$ and $\mu\textsubscript{R}$ are the mean intensities within the two windows, and $\delta_x$ is the displacement (disparity) of window W\textsubscript{R} relative to W\textsubscript{L}. This way, the correct disparity for each object in stereo images can be computed. The problem is that this method also computes the correct non-degraded disparity even if the crosstalk is induced to the images. This does not correspond well to the HVS behavior. Hence we need an HVS model that can simulate not only the correct disparity estimation but also the degraded disparity when crosstalk is added to the images. \textcolor{red}{Mention the disparity gradient as explained in this paper in the discussion.}

\section{Reduction of crosstalk}

As mentioned in the previous sections, crosstalk severely hinders the perceived depth and reduces the overall visual quality and viewer comfort. Hence it is imperative for the crosstalk levels to be mitigated or at least lowered to an unperceivable level. Almost all of the 3D displays using present hardware technologies have some amount of crosstalk present in them. Fortunately it is possible to calculate the amount of leakage between views at any position for any display. Usually a luminance meter is used to detect the amount of light leaked between views. Once the leakage levels for a display system are computed, image processing techniques can used to preprocess the stereo images in such a way that results in mitigation or minimization of the perceived ghosting once they are displayed on any traditional 3D screen.Early attempts relied on subtracting from one view image, the leaked image intensity from other perspective view before displaying. This technique might result in  negative light intensities in low contrast areas of the images. Since negative light can not be produced by any display, the areas of the preprocessed image that has negative intensities are clamped to zero. Which means that the crosstalk in these areas is not fully subtracted and hence the ghosting still persists. One way to avoid such problem is to increase the overall image intensity by some value such that no negative values are obtained after crosstalk subtraction. This however comes at a cost of decreased average contrast of an image hence degrading the overall image quality. In the following sections we will review some of the contemporary techniques that are used in order to remove the crosstalk as well as maintaining the overall image quality.

\subsection{Stereoscopic screens}

 Konard et al \cite{konrad2000cancellation} proposed a crosstalk reduction technique that took the ghosting perception thresholds into consideration.For every possible combination of crosstalk level and the contrast of the scene, they experimentally computed the minimum level of light intensity that after subtraction would bring the ghosting to an undetectable level by a human observer. Ghosting was later minimized efficiently by storing and using these values in a lookup table. In order to avoid the negative light intensity values after crosstalk subtraction, they proposed to increase all the pixel values by the maximum negative intensity obtained hence reducing the overall image contrast. Limpscomb and Wooten \cite{lipscomb1994reducing} took the specially non-uniform nature of crosstalk in the display into consideration and proposed a technique that consisted of dividing the screen into 16 horizontal bands. The crosstalk was evaluated for each of these bands followed by the crosstalk subtraction in the images accordingly. The problem with this technique is that the non uniformity of the crosstalk level between and across the bands is continuous in nature which is why it resulted in over and under subtraction of crosstalk between bands that was still perceivable by the viewers. Another problem is that all of the above mentioned techniques assumes static scenes and hence ignore the temporal aspects. In a time sequential displays, crosstalk is induced not only by the view image from the opposite aspect (i.e. left and right view) but also from the views in the previous frame. Smit et al \cite{smit2007non} took this phenomenon into consideration as well. However, as the problem with every subtractive approach, this technique also suffered from the over subtraction. Sohn and Jung \cite{sohn2014crosstalk} proposed a technique that utilized disparity adjustments for a scene such that the least amount of uncorrectable crosstalk occurs in perceptually important regions. A crosstalk visibility estimator that simulated human sensitivity to luminance changes according to Webber's law was used in order to determine the areas in a scene where the spatio-temporal crosstalk was visible. In the second step, the global disparities in the scene were changed (shifting the zero plane) and the amount of perceivable uncorrectable crosstalk was computed using the crosstalk visibility estimator for every step. The disparity that yielded the lowest amount of uncorrectable visually important crosstalk were chosen for displaying. In order to remove the already minimized uncorrectable crosstalk, the intensities in the scenes was locally increased in order to preserve as much dynamic range as possible.

 Most recently, Baar and Poulakos et at \cite{van2011perceptually}


\subsection{Automultiscopic screens}
\subsubsection{Inverse filtering}
\subsubsection{Subtractive reduction}
\subsubsection{Sub-pixel optimization}
\subsubsection{Low Pass filtering}